Literature Review - Informal

### 2019-12-19 Literature Review/Literature Review - Informal/sample.tex
Nothing important changed

\textbf{Francesco: I've moved this to the top for your attention - it seems to be the most
interesting problem with the scope to improve the theoretical results as well as applications in
complex domains which are of significant interest these days. I will be adding in the
state-of-the-art review as we go along, but for now the general overview and research directions
are provided.}

@@

@@

\begin{itemize}
	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
	interact with each other. In addition, we may consider that there are multiple known disturbances
	acting on the system. This, at first seems like an impossible problem to solve due to the many
	interactions between all elements of the system. However, we can consider this as a game
	theoretic problem in which the components and the disturbances are players. The relatively new
	class of 'mean-field games' is a method which allows the many body problem to be approximated as
	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
	predictive control' remain, this may prove to be a valuable area of applied research.
	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
	which emerge into more complex results. It would be interesting to consider the application of
	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
	adaptive stochastic model would be interesting to examine here to remain robust to agent
	failures in the group.
\end{itemize}

@@

The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
particularly relevant to this study. However, they will require some further analysis before I write
about them here.

>>>>

@@

The research in using Distributed Predictive Control is quite sparse as compared with, for example,
single agent predictive control. The added complexity of stochastic environments has meant that this
area of research is still very open for looking into. With this said, the main works that I have
found useful whilst reviewing the literature are \cite{Conte2014}, \cite{Christofides2013} and 
\cite{Giulioni2015}. In almost all of the presented methods, a number of assumptions are made.
Usually these are some combination of the following:

\begin{itemize}
	\item The agents act in a deterministic environment. This suggests that predicted futures will
	be close enough to the ground truth.
	\item The agents are uncoupled from one another. This is a strong assumption to make and
	essentially allows us to consider the agents as completely independent of one another. 
	\item The agents can easily communicate with one another. This allows for longer pieces of
	communication (most often predicted trajectories) to be communicated between agents.
\end{itemize}

@@

\begin{itemize}
	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
	interact with each other. In addition, we may consider that there are multiple known disturbances
	acting on the system. This, at first seems like an impossible problem to solve due to the many
	interactions between all elements of the system. However, we can consider this as a game
	theoretic problem in which the components and the disturbances are players. The relatively new
	class of 'mean-field games' is a method which allows the many body problem to be approximated as
	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
	predictive control' remain, this may prove to be a valuable area of applied research.
	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
	which emerge into more complex results. It would be interesting to consider the application of
	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
	adaptive stochastic model would be interesting to examine here to remain robust to agent
	failures in the group.
	\item Modular Robotics?
\end{itemize}

@@

The following papers \cite{Bailey2019FiniteDescent-Ascent, Bailey2019Multi-AgentSystem,
Boone2019FromTheory, DickensTheLearning, Berkenkamp2017SafeGuarantees,
Jin2018Stability-certifiedPerspective, Letcher2019DifferentiableMechanics} are the ones that I found
particularly relevant to this study. However, they will require some further analysis before I write
about them here. (Note: I've written about some of these in the paragraphs above, but I'm not
entirely sure which ones yet. I think the job over Christmas will mainly be about sorting this
document out.)

\chapter{Research Directions}

\section{Stochastic Model Predictive Control for Distributed Systems}

The work on distributed stochastic MPC (DSMPC) is still rather sparse but is advancing rapidly. To
that end, I propose the following techniques towards improving DSMPC.

\begin{itemize}
	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
	distribution of the action that will likely be selected by $j$, effectively performing a
	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
	this may seem computationally expensive, its advantage lies in the fact that it requires little
	communication across the agents. An immediate disadvantage of this is that, as the number of
	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
	not yet confident on the feasibility or the usefulness of this technique, but looking further
	into the literature (which seems to add new things every day) may provide insights which could
	help refine the technique. This method is, in many ways, similar to that presented in 
	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
	all systems to update at each time step.

	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
	public belief based on the observed actions of all agents. This joint belief will likely provide
	some representation of the trajectories that each agent will carry out or an understanding of
	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
	will be chosen from a family of existing models using a recursive Bayesian update. The idea
	would be for this update to be conditioned on the history of observations as is done in 
	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
	state and use this, in combination with their own system models to determine a feasible
	trajectory. The challenge here would be proving the stability and controllability of the system
	and that it requires communication with a central controller. However, it would appear to be a
	feasible area of exploration.
\end{itemize}

\section{Stochastic Control of Swarms}

Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
when considering its application in stochastic environments. In particular, the ideas presented
below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
desired distribution.

\begin{itemize}
	\item Consideration of state constraints or boundary conditions (terms which I will use
interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
particular stochastic difference equation (the Ito equation). However, this does not account for any
boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
obstacle avoidance. However, in environments where there are human operators, or in general areas
where we do not want swarms to enter, it is important to have a guarantee of constraint
satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
Furthermore, it may present an opportunity for us to consider the decentralised control of the
agents which can ensure state constraint satisfaction. The resources which are most relevant to this
study (and from which the ideas are derived) are
\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.

\item Consideration of pairwise interactions between agents to ensure collision avoidance. Most of
the diffusion models, as mentioned above, do not take into consideration the interactions between
agents, since it adds a large degree of complexity to the model. However, it would be important from
a safety perspective to take these into account by looking at the attractive and repulsive
potentials across agents. This would allow us to provide a guarantee of inter-agent collision
avoidance whilst maintaining the diffusive progress of the swarm. In \cite{Inoue2019}, the authors
mention that they are already looking into this problem and have proposed a similar manner of
tackling it as I have. Perhaps we may be able to build upon or improve their results if and when
they publish?

\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
number of their nearest neighbours. However, this may not always be the case. It will often be that
in different environmental conditions, the observation or communication capabilities of the robots
may increase or decrease. To better accomodate for this fact, I propose the extension of the model
with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
way into swarm dynamics. It will, however, become particularly important in cases where we can no
longer take the consistency of agent communication for granted. 
\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
not seem like the connection of MJD and swarm dynamics has been made yet.
\end{itemize}

\section{Multi Agent Reinforcement Learning}

The ideas I have down here are a little more sparsely populated, but further reading may provide
some insights into potential directions.

\begin{itemize}
	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
	required that we determine a safe manner in which MARL agents may explore without leading to
	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
	independent learners who do not consider the effect that they have on the other agent(s). The
	particular extension that I propose is to consider the coupled effect between agents as part of
	the determination of a safe set for exploration.

	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
	problems. Although it makes strong assumptions about the nature of the system, in practice it
	has shown strong results. Particular examples of this are found in 
	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
	systems by considering sub-groups within the population. Each of these may be updated
	individually. It would be interesting to examine how this might increase the complexity, and
	also the generalisability of the mean-field method.
	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
	part but the potential directions are largely summarised in Section 2.3.1.
\end{itemize}
